Refining from the BON High-level Specification Language to the VHDL-AMS Hardware Description Language

### 2009-08-26 papers/BON_VHDL/paper.tex
correction

%======================================================================
\section{Introduction}
\label{sec:introduction}
The \ST sensor platform, represents heterogeneous collection of digital, analog 
and mixed signal hardware circuits. Embedded system complexity 
requires the need to strive for formal descriptions each component 
separatelly in order to produce specification of the \STS. 
Our aim is to be able to precisely describe the structures of circuits,
the behaviour of circuits and the formal link between structures and behaviours.
In other words, the behavioural specification of the \STS may be 
specified as a \inv on the signals at the circuit's ports and may be obtained 
by taking the conjunction of the \emph{invariants} that describe 
behaviours of the individual components separately. 
For this purpose we need  sophisticated tool and methodology 
in order to be able to achieve this goal.  
The authors will illustrate in this article how BON can represent a high 
level analogue mapping and will further illustrate a procedure for 
transformation from VHDL-AMS to BON.\\ 
This article provides two main contributions.
\begin{enumerate}
\item 
 It provides a solution how to formally emulate
 piece of hardware using BON-JML approach; up to date BON and JML
 has been used mostly in the pure object oriented software construction.    
\item
It relates hardware description code and formal calculus. 
This means that if there  is a code that is "correct by construction", 
then it will be derivable from BON (informal/formal) specification, 
via the refinement calculus to JML implementation.     
\end{enumerate}
The rest of this article is organized as follows.
In \autoref{sec:vhdlams} we have  presented an overview of VHDL-AMS language.
\autoref{sec:choiceobon} defines  BON principles and explains the 
reasons why we have decided to use BON method.
The central part of the our article is \autoref{sec:mappingVB}, which 
shows mapping between VHDL-AMS and BON. 
In \autoref{sec:refVB} we will give practical aspect of refinement, 
applied on real capacitor component, in order to produce formal specification  
and software simulation.\\  
A comprehensive list of the mapping between BON and VHDL-AMS can be 
found in the appendix.
%=====================================================================

>>>>

%======================================================================
\section{Introduction}
\label{sec:introduction}
The \ST sensor platform, represents heterogeneous collection of digital, analog 
and mixed signal hardware circuits. Embedded system complexity 
requires the need to strive for formal descriptions each component 
separatelly in order to produce specification of the \STS. 
Our aim is to be able to precisely describe the structures of circuits,
the behaviour of circuits and the formal link between structures and behaviours.
In other words, the behavioural specification of the \STS may be 
represented as a \inv on the signals at the circuit's ports and may be obtained 
by taking the conjunction of the \emph{invariants} that describe 
behaviours of the individual components separately. 
For this purpose we need  sophisticated tool and methodology 
in order to be able to achieve this goal.  
The authors will illustrate in this article how BON can represent a high 
level analogue mapping and will further illustrate a procedure for 
transformation from VHDL-AMS to BON.\\ 
This article provides two main contributions.
\begin{enumerate}
\item 
 It provides a solution how to formally emulate
 piece of hardware using BON-JML approach; up to date BON and JML
 has been used mostly in the pure object oriented software construction.    
\item
It relates hardware description code and formal calculus. 
This means that if there  is a code that is "correct by construction", 
then it will be derivable from BON (informal/formal) specification, 
via the refinement calculus to JML implementation.     
\end{enumerate}
The rest of this article is organized as follows.
In \autoref{sec:vhdlams} we have  presented an overview of VHDL-AMS language.
\autoref{sec:choiceobon} defines  BON principles and explains the 
reasons why we have decided to use BON method.
The central part of the our article is \autoref{sec:mappingVB}, which 
shows mapping between VHDL-AMS and BON. 
In \autoref{sec:refVB} we will give practical aspect of refinement, 
applied on real capacitor component, in order to produce formal specification  
and software simulation.\\  
A comprehensive list of the mapping between BON and VHDL-AMS can be 
found in the appendix.
%=====================================================================
